Tugas UTS

### 2024-02-26 Project/Tugas UTS.Rmd
Update

```{r}
n<-nrow(d1)
teta_hat<-mean(d1$item1)/ 
(mean(d1$item1)+mean(d1$item2))
y<-matrix(NA,n,n-1)
x<-matrix(NA,n,n-1)
for (i in 1:n) {
y[i,]<-d1$item1[-i]
x[i,]<-d1$item2[-i]
}
ybar<-apply(y,1,mean)
xbar<-apply(x,1,mean)
teta_i<-ybar/(xbar+ybar)
teta_jk<-n*teta_hat-(n-1)*mean(teta_i)
var_jk<-(n-1)/n*(sum(teta_i^2)-(n*mean(teta_i)^2))
se_jk<-sqrt(var_jk)
teta_jk;var_jk;se_jk
```

@@

```{r}

```

>>>>

```{r}
n <- nrow(d1)
teta_hat <- mean(d1$item1)/ (mean(d1$item1) +mean(d1$item2))
y <- matrix(NA,n,n-1)
x <- matrix(NA,n,n-1)
for (i in 1:n) {
  y[i,] <- d1$item1[-i]
  x[i,] <- d1$item2[-i]
}
ybar <- apply(y,1,mean)
xbar <- apply(x,1,mean)
teta_i <- ybar/ (xbar+ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)
var_jk <- (n-1)/ n *(sum(teta_i^2) -(n *mean(teta_i)^2))
se_jk <- sqrt(var_jk)
teta_jk; var_jk; se_jk
```

@@

# Perbandingan Semua Cara

```{r}
d1 <- dataCity
n <- nrow(d1)
teta_hat <- mean(d1[,1])/ (mean(d1[,1]) +mean(d1[,2]))
y <- matrix(NA, n, n-1)
x <- matrix(NA, n, n-1)

for (i in 1:n) {
  y[i,] <- d1[,1][-i]
  x[i,] <- d1[,2][-i]
}

ybar <- apply(y, 1, mean)
xbar <- apply(x, 1, mean)

teta_i <- ybar/ (xbar +ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)

var_jk <- (n-1)/ n *(sum(teta_i^2) -(n *mean(teta_i)^2))
se_jk <- sqrt(var_jk)

teta_jk; var_jk; se_jk
```
